HPC--101\\Onboarding

### 2019-06-15 hpc_101/sections/01_intro.tex
revised slides to correct wording and reduce number of slides

\begin{frame}
	\frametitle{Terminology}
	\begin{itemize}
	\item \textbf{Symbolic Link (symlink)} -- A file that contains a reference to another file or directory
	\item \textbf{Command-line interface (CLI)} -- A text-based user interface used to view and manage computer files 
	\item \textbf{Message Passing Interface (MPI)} -- A standard that is used by programs to pass messages between nodes
	\item \textbf{High Performance Compute (HPC)} -- A computing paradigm in which applications are typically a tightly coupled parallel job that benefit from a low-latency interconnect
	\item \textbf{High Throughput Compute (HTC)} -- A computing paradigm that focuses on the efficient execution of a large number of loosely-coupled tasks
%	      \item Pleasantly Parallel -- Processes are independent and no communication is necessary 
	\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Terminology}
	\begin{itemize}
	\item \textbf{Symbolic Link (symlink)} -- A file that contains a reference to another file or directory
	\item \textbf{Command-line interface/interpreter (CLI)} -- A text-based user interface used to view and manage computer files 
	\item \textbf{Message Passing Interface (MPI)} -- A standard that is used by programs to pass messages between nodes
	\item \textbf{High Performance Compute (HPC)} -- A computing paradigm in which applications are typically a tightly coupled parallel job that benefit from a low-latency interconnect
	\item \textbf{High Throughput Compute (HTC)} -- A computing paradigm that focuses on the efficient execution of a large number of loosely-coupled tasks
        \item \textbf{Modified time} -- The last time the file was modified (content has been modified)\footnote{\label{Types of timestamps}\tiny\url{https://unix.stackexchange.com/a/2465}}
        \item \textbf{Shell script (script)} -- A computer program designed to be run by a CLI\footnote{\label{Shell script}\tiny\url{https://en.wikipedia.org/wiki/Shell_script}}
%        \item Pleasantly Parallel -- Processes are independent and no communication is necessary 
	\end{itemize}
